### 2023-11-09 main.tex
''

\begin{theorem}[Absorbing duality]

@@

\subsection{Proof of duality}

@@

%In this notation, the elements of the duality matrix reads
%\begin{equation}\label{ElementsDualityMatrixChain_1}
%	D(\bm{\tau},\bm{\xi})=\prod_{a=1}^{N-1}\alpha_{a}^{\xi_{a}^{0}}\left(\prod_{x=1}^{L}\prod_{a=1}^{N-1}\mathbbm{1}_{\{\delta_{\tau_{x},a}\geq \xi_{a}^{x}\}}\right)\prod_{a=1}^{N-1}\beta_{a}^{\xi_{a}^{L+1}}\dt
%\end{equation}
%\\
Using the above duality elements, we can compute the  $m$-point correlations between non-empty particles using the absorption probabilities. For arbitrary $m\in \mathbb{N}$ such that $m<L$, we fix $a_{k}\in\{1,\ldots,N-1\}$ and $x_{k}\in\{1,\ldots,L\}$ such that $x_{k}<x_{k+1}$ for every $k\in\{1,\ldots,m\}$. We pick the dual configuration $\xi=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$, meaning that 
\begin{equation}
	\begin{cases}
		\xi_{a}^{x}=1\qquad \text{if}\;x=x_{k}\;\text{and}\; a=a_{k}\\
		\xi_{a}^{x}=0\qquad \text{otherwise}
	\end{cases}
\end{equation}
For any $\bm{\tau}\in \Omega$ the elements of the duality matrix defined in \eqref{ElementsDualityMatrixChain_1} read
\begin{equation}
	D(\bm{\tau},\bm{\xi})%=\prod_{k=1}^{m}\mathbbm{1}_{\{\delta_{\tau_{x_{k}},a_{k}}=1\}}
	=\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\dt
\end{equation}
For the $m$-point correlations in the non-equilibrium steady state (NESS) we have, by duality,
%To compute the steady state $m$-point correlations of the process $\bm{n}(t)$ we recall that the dual process eventually voids the chain (by putting all particles in the extra-sites $0$ and $L$). Therefore, we have the following equalities
\begin{equation}\label{CorrelationByABS-prob}
	\begin{split}
\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]&=\lim_{t\to \infty}\mathbb{E}_{\bm{\tau}}\left[D(\bm{\tau}(t),\bm{{\xi}})\right]=\lim_{t\to \infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{\tau},\bm{{\xi}}(t))\right]
	\\&=\sum_{t_{1}=0}^{1}\ldots \sum_{t_{m}=0}^{1}\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\mathcal{P}(t_{1},\ldots,t_{m},\bm{\xi})
\end{split}
\end{equation}
where
\begin{equation}\label{absProbabilitiesIntegrable}
	\mathcal{P}(t_{1},\ldots,t_{m},\bm{\xi}):=\mathbb{P}\left(\bm{\xi}(\infty)=\sum_{k=1}^{m}\left(t_{k}\delta^{0}_{a_k}+(1-t_{k})\delta^{L+1}_{a_k}\right)\lvert \bm{\xi}(0)=\bm{\xi}\right)
\end{equation}
 is the  probability that  $t_{k}$ particles of species $a_{k}$ (initially positioned at site $x_{k}$) are absorbed at the extra site $\{0\}$. Therefore, by computing these absorption probabilities we determine the non-equilibrium steady state correlations of the integrable multi-species stirring process.

@@

 The first transformation $S_{1}$ is closely related to the duality matrix and we will see that $H^{'}$ is $\widetilde{H}^{T}$, up to the extra-site term described by the bosonic creation operator in \eqref{siteDualHamiltonian}. Therefore, $H^{'}$ is not stochastic. The second transformation $S_{2}$ diagonalizes the right boundary. Finally, the composition  $S_{2} S_{1}$ allows to simplify the commutators of the MPA algebra. 
\subsection{Explicit correlations in the non-equilibrium steady state}\label{subsection-exact}
In this section we write a formula for the stationary non-equilibrium steady state correlations between $m$- points of the chain, each of them occupied by a non-empty species, i.e. a species with label from $1$ to $N-1$.
\begin{theorem}\label{thm-correlations}[Explicit non-equilibrium steady state correlations]
Consider $m\in \{1,\ldots,L\}$ points with coordinates given by $(x_{1},\ldots,x_{m})$, such that $x_{k}<x_{k+1}$ $\forall k\in \{1,\ldots,m-1\}$. We assume that in each of these points there is a particle of species $a_{k}\in \{1,\ldots,N-1\}$. Then the $m$-point correlations with respect to the non-equilibrium steady state measure $\mu^{NESS}$ are given by 
\begin{equation}\label{exactCorrelations}
	\begin{split}
		&\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]\\=&\sum_{t_{1},\ldots,t_{m}=0}^{1}\left(\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\right)\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}f(L,c_{1},\ldots,c_{m})\left(\prod_{k=1}^{m}(-1)^{c_{k}-t_{k}}g_{k}(L,x_{k},c_{k},\ldots,c_{m})\right)
		\end{split}
\end{equation}
where
\begin{equation}\label{powerCoeffSpecies}
	g_{k}(L,x_{k},c_{k},\ldots,c_{m})=\left(L+2-x_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}
\end{equation}
and 
\begin{equation}\label{powerCoeffNOspec}
	f(L,c_{1},\ldots,c_{m})=\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{a})}{\Gamma(2+L)}
\end{equation}
Moreover, the absorption probabilities defined in \eqref{absProbabilitiesIntegrable} are
\begin{equation}\label{abs-probabilities}
	\mathcal{P}(t_{1},\ldots,t_{m},\bm{\xi})=\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}f(L,c_{1},\ldots,c_{m})\prod_{j=1}^{m}(-1)^{c_{j}-t_{j}}g_{j}(L,x_{j},c_{j},\ldots,c_{m})
\end{equation}
where $\bm{\xi}=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$.
\end{theorem}
\begin{comment}
 Consider . . Then, with respect to the non-equilibrium stationary distribution, the correlations among these particles are given by
\begin{equation}\label{exactCorrelations}
	\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=\sum_{c_{1},\ldots,c_{m}=0}^{1}
	f(L,c_{1},\ldots,c_{m})\prod_{k=1}^{m}(\alpha_{a_{k}}-\beta_{a_{k}})^{c_{k}}\beta_{a_{k}}^{1-c_{k}}g_{k}(L,y_{k},c_{k},\ldots,c_{m})
\end{equation}
\end{comment}
\begin{comment}
where 
\begin{equation}\label{powerCoeffSpecies}
	g_{k}(L,x_{k},c_{k},\ldots,c_{m})=\left(L+2-x_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}
\end{equation}
and 
\begin{equation}\label{powerCoeffNOspec}
	f(L,c_{1},\ldots,c_{m})=\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{a})}{\Gamma(2+L)}
\end{equation}
\end{comment}

	\begin{remark}
		The non-equilibrium steady state correlations can also be written as 
			\begin{equation}\label{exactCorrelation_1}
			\begin{split}
				\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]=&\frac{1}{(1+L)!}\sum_{c_{y_{1}},\ldots,c_{y_{m}}=0}^{1}\prod_{k=1}^{m}(\alpha_{s_{k}}-\beta_{s_{k}})^{1-c_{y_{k}}}\beta_{s_{k}}^{c_{y_{k}}}\left(2+L-y_{k}-\sum_{j=k}^{m}(1-c_{y_{j}})\right)\\&\prod_{x=1\,:\,x\notin \{y_{1},\ldots,y_{m}\}}^{L}\left(2+L-x-\sum_{k=1}^{m}\mathbbm{1}_{\{x<y_{k}\}}(1-c_{y_{k}})\right)
			\end{split}
		\end{equation}
\end{remark}
\begin{comment}
\paragraph{Absorption probabilities}
Knowing the non-equilibrium steady state correlations, we can read-off the absorption probabilities defined in \eqref{absProbabilitiesIntegrable}. They are given by
\begin{equation}\label{abs-probabilities}
	\mathcal{P}(t_{1},\ldots,t_{m},\bm{\xi})=\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}f(L,c_{1},\ldots,c_{m})\prod_{j=1}^{m}(-1)^{c_{j}-t_{j}}g_{j}(L,x_{j},c_{j},\ldots,c_{m})
\end{equation}
. \\ \\
\textbf{Proof of \eqref{abs-probabilities}}: 
From \eqref{exactCorrelations} we have

@@

The average with respect to the non equilibrium distribution of the occupation variable of the species $a_{1}\in \{1,\ldots,N-1\}$ at coordinate $x_{1}\in \{1,\ldots,L\}$ reads
\mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\right]=\sum_{c_{1}=0}^{1}f(L,c_{1})(\alpha_{a_{1}}-\beta_{a_{1}})^{c_{1}}\beta_{a_{1}}^{1-c_{1}}g_{a_{1}}(L,x_{1},c_{1})\dt
Using \eqref{powerCoeffSpecies} and \eqref{powerCoeffNOspec} we obtain 

@@

	 \mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\right]=\frac{(L+1-y_{1})}{L+1}(\alpha_{a_{1}}-\beta_{a_{1}})+\beta_{a_{1}}\dt

@@

The two-point correlations with respect to the non equilibrium distribution of the occupation variable of the species $a_{1},a_{2}\in \{1,\ldots,N-1\}$ at coordinates $x_{1},x_{2}\in \{1,\ldots,L\}$ with $x_{1}< x_{2}$ reads 
		 \mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\right]= \sum_{c_{1}=0}^{1}\sum_{c_{2}=0}^{1}f(L,c_{1},c_{2})\prod_{k=1}^{2}(\alpha_{a_{k}}-\beta_{a_{k}})^{c_{k}}\beta_{a_{k}}^{1-c_{k}}g_{k}(L,x_{k},c_{k},c_{2})\dt
Using \eqref{powerCoeffSpecies} and \eqref{powerCoeffNOspec} we obtain 

@@

The three-point correlations with respect to the non equilibrium distribution of the occupation variable of the species $a_{1},a_{2},a_{3}\in \{1,\ldots,N-1\}$ at coordinates $x_{1},x_{2},x_{3}\in \{1,\ldots,L\}$ such that $x_{1}<x_{2}<x_{3}$
 \mathbb{E}_{\mu^{NESS}}\left[\prod_{k=1}^{3}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=\sum_{c_{1}=0}^{1}\sum_{c_{2}=0}^{1}\sum_{c_{3}=0}^{1}f(L,c_{1},c_{2},c_{3})\prod_{k=1}^{3}(\alpha_{a_{k}}-\beta_{a_{k}})^{c_{k}}\beta_{a_{k}}^{1-c_{k}}g_{k}(L,x_{k},c_{k},\ldots,c_{3})\dt
Using \eqref{powerCoeffSpecies} and \eqref{powerCoeffNOspec} we obtain 

>>>>

\begin{theorem}[Absorbing duality]\label{thm-duality}

@@

\subsection{Proof of Theorem \ref{thm-duality}}

@@

%In this notation, the elements of the duality matrix reads
%\begin{equation}\label{ElementsDualityMatrixChain_1}
%	D(\bm{\tau},\bm{\xi})=\prod_{a=1}^{N-1}\alpha_{a}^{\xi_{a}^{0}}\left(\prod_{x=1}^{L}\prod_{a=1}^{N-1}\mathbbm{1}_{\{\delta_{\tau_{x},a}\geq \xi_{a}^{x}\}}\right)\prod_{a=1}^{N-1}\beta_{a}^{\xi_{a}^{L+1}}\dt
%\end{equation}
%\\
Using the above duality elements, we can compute the  $m$-point correlations between non-empty particles using the absorption probabilities. Therefore, to determine the non-equilibrium steady state correlations of the integrable multi-species stirring process, it is enough to compute these absorption probabilities.  %For arbitrary $m\in \mathbb{N}$ such that $m<L$, we fix $a_{k}\in\{1,\ldots,N-1\}$ and $x_{k}\in\{1,\ldots,L\}$ such that $x_{k}<x_{k+1}$ for every $k\in\{1,\ldots,m\}$. 
\begin{proposition}[Correlations via duality]
Consider $m\in \{1,\ldots,L\}$ and let $a_{k}\in\{1,\ldots,N-1\}$ species positioned at sites $x_{k}\in\{1,\ldots,L\}$ such that $x_{k}<x_{k+1}$. Then, the $m$-point correlations in the non-equilibrium steady state (NESS) read
\begin{equation}
\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=\sum_{t_{1}=0}^{1}\ldots \sum_{t_{m}=0}^{1}\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\mathcal{P}(t_{1},\ldots,t_{m},\bm{\xi})
\end{equation}
where
\begin{equation}\label{absProbabilitiesIntegrable}
	\mathcal{P}(t_{1},\ldots,t_{m},\bm{\xi}):=\mathbb{P}\left(\bm{\xi}(\infty)=\sum_{k=1}^{m}\left(t_{k}\delta^{0}_{a_k}+(1-t_{k})\delta^{L+1}_{a_k}\right)\lvert \bm{\xi}(0)=\bm{\xi}\right)
\end{equation}
is the  probability that  $t_{k}$ particles of species $a_{k}$ (initially positioned at site $x_{k}$) are absorbed at the extra site $\{0\}$. The dual configuration is $\bm{\xi}=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$, meaning that 
\begin{equation}
	\begin{cases}
		\xi_{a}^{x}=1\qquad \text{if}\;x=x_{k}\;\text{and}\; a=a_{k}\\
		\xi_{a}^{x}=0\qquad \text{otherwise}
	\end{cases}
\end{equation}
\end{proposition}
\textbf{Proof}:
For any $\bm{\tau}\in \Omega$ the elements of the duality matrix defined in \eqref{ElementsDualityMatrixChain_1} read
\begin{equation}
	D(\bm{\tau},\bm{\xi})%=\prod_{k=1}^{m}\mathbbm{1}_{\{\delta_{\tau_{x_{k}},a_{k}}=1\}}
	=\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\dt
\end{equation}
Therefore, by duality we have 
\begin{equation}\label{CorrelationByABS-prob}
	\begin{split}
\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]&=\lim_{t\to \infty}\mathbb{E}_{\bm{\tau}}\left[D(\bm{\tau}(t),\bm{{\xi}})\right]=\lim_{t\to \infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{\tau},\bm{{\xi}}(t))\right]
	\\&=\sum_{t_{1}=0}^{1}\ldots \sum_{t_{m}=0}^{1}\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\mathcal{P}(t_{1},\ldots,t_{m},\bm{\xi})
\end{split}
\end{equation}
\begin{flushright}
	$\square$
\end{flushright}

@@

 The first transformation $S_{1}$ is closely related to the duality matrix and we will see that $H^{'}$ is $\widetilde{H}^{T}$, up to the extra-site term described by the bosonic creation operator in \eqref{siteDualHamiltonian}. Therefore, $H^{'}$ is not stochastic. The second transformation $S_{2}$ diagonalizes the right boundary. Finally, the composition  $S_{2} S_{1}$ allows to simplify the commutators of the MPA algebra. 
\subsection{Explicit correlations in the non-equilibrium steady state}\label{subsection-exact}
In this section we write a formula for the stationary non-equilibrium steady state correlations between $m$- points of the chain, each of them occupied by a non-empty species, i.e. a species with label from $1$ to $N-1$.
\begin{theorem}[Explicit non-equilibrium steady state correlations]\label{thm-correlations}
Consider $m\in \{1,\ldots,L\}$ points with coordinates given by $(x_{1},\ldots,x_{m})$, such that $x_{k}<x_{k+1}$ $\forall k\in \{1,\ldots,m-1\}$. We assume that in each of these points there is a particle of species $a_{k}\in \{1,\ldots,N-1\}$. Then the $m$-point correlations with respect to the non-equilibrium steady state measure $\mu^{NESS}$ are given by 
\begin{equation}\label{exactCorrelations}
	\begin{split}
		&\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]\\=&\sum_{t_{1},\ldots,t_{m}=0}^{1}\left(\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\right)\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}f(L,c_{1},\ldots,c_{m})\left(\prod_{k=1}^{m}(-1)^{c_{k}-t_{k}}g_{k}(L,x_{k},c_{k},\ldots,c_{m})\right)
		\end{split}
\end{equation}
where
\begin{equation}\label{powerCoeffSpecies}
	g_{k}(L,x_{k},c_{k},\ldots,c_{m})=\left(L+2-x_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}
\end{equation}
and 
\begin{equation}\label{powerCoeffNOspec}
	f(L,c_{1},\ldots,c_{m})=\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{a})}{\Gamma(2+L)}
\end{equation}
Moreover, the absorption probabilities defined in \eqref{absProbabilitiesIntegrable} are
\begin{equation}\label{abs-probabilities}
	\mathcal{P}(t_{1},\ldots,t_{m},\bm{\xi})=\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}f(L,c_{1},\ldots,c_{m})\prod_{j=1}^{m}(-1)^{c_{j}-t_{j}}g_{j}(L,x_{j},c_{j},\ldots,c_{m})
\end{equation}
where $\bm{\xi}=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$.
\end{theorem}
\begin{comment}
 Consider . . Then, with respect to the non-equilibrium stationary distribution, the correlations among these particles are given by
\begin{equation}\label{exactCorrelations}
	\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=\sum_{c_{1},\ldots,c_{m}=0}^{1}
	f(L,c_{1},\ldots,c_{m})\prod_{k=1}^{m}(\alpha_{a_{k}}-\beta_{a_{k}})^{c_{k}}\beta_{a_{k}}^{1-c_{k}}g_{k}(L,y_{k},c_{k},\ldots,c_{m})
\end{equation}
\end{comment}
\begin{comment}
where 
\begin{equation}\label{powerCoeffSpecies}
	g_{k}(L,x_{k},c_{k},\ldots,c_{m})=\left(L+2-x_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}
\end{equation}
and 
\begin{equation}\label{powerCoeffNOspec}
	f(L,c_{1},\ldots,c_{m})=\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{a})}{\Gamma(2+L)}
\end{equation}
\end{comment}

	\begin{remark}
		The non-equilibrium steady state correlations can also be written as 
			\begin{equation}\label{exactCorrelation_1}
			\begin{split}
				\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=&\frac{1}{(1+L)!}\sum_{c_{x_{1}},\ldots,c_{x_{m}}=0}^{1}\prod_{k=1}^{m}(\alpha_{a_{k}}-\beta_{a_{k}})^{1-c_{x_{k}}}\beta_{a_{k}}^{c_{x_{k}}}\left(2+L-x_{k}-\sum_{j=k}^{m}(1-c_{x_{j}})\right)\\&\prod_{x=1\,:\,x\notin \{x_{1},\ldots,x_{m}\}}^{L}\left(2+L-x-\sum_{k=1}^{m}\mathbbm{1}_{\{x<y_{k}\}}(1-c_{x_{k}})\right)
			\end{split}
		\end{equation}
\end{remark}
\begin{comment}
\paragraph{Absorption probabilities}
Knowing the non-equilibrium steady state correlations, we can read-off the absorption probabilities defined in \eqref{absProbabilitiesIntegrable}. They are given by
\begin{equation}\label{abs-probabilities}
	\mathcal{P}(t_{1},\ldots,t_{m},\bm{\xi})=\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}f(L,c_{1},\ldots,c_{m})\prod_{j=1}^{m}(-1)^{c_{j}-t_{j}}g_{j}(L,x_{j},c_{j},\ldots,c_{m})
\end{equation}
. \\ \\
\textbf{Proof of \eqref{abs-probabilities}}: 
From \eqref{exactCorrelations} we have

@@

We consider the average with respect to $\mu^{NESS}$ of the occupation variable of the species $a_{1}\in \{1,\ldots,N-1\}$ at coordinate $x_{1}\in \{1,\ldots,L\}$. %This reads
%\mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\right]=\sum_{t_{1}=0}^{1}\alpha_{a_{1}}^{t_{1}}\beta_{a_{1}}^{1-t_{1}}\sum_{c_{1}=t_{1}}^{1}f(L,c_{1})g_{a_{1}}(L,x_{1},c_{1})\dt
Using \eqref{abs-probabilities} we obtain the absorption probabilities 
	\mathcal{P}(0,\bm{\xi})=1-\frac{(L+1-x_{1})}{(1+L)}\qquad \mathcal{P}(1,\bm{\xi})=\frac{(L+1-x_{1})}{(1+L)}
where $\bm{\xi}=\delta_{a_{1}}^{x_{1}}$. Then, using \eqref{exactCorrelations}, we have

@@

	 \mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\right]=\frac{(L+1-x_{1})}{L+1}(\alpha_{a_{1}}-\beta_{a_{1}})+\beta_{a_{1}}\dt

@@

We consider the average with respect to $\mu^{NESS}$ of the occupation variable of the species  $a_{1},a_{2}\in \{1,\ldots,N-1\}$ at coordinates $x_{1},x_{2}\in \{1,\ldots,L\}$ such that $x_{1}< x_{2}$. 
%		 \mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\right]= \sum_{t_{1}=0}^{1}\sum_{t_{2}=0}^{1}\left(\prod_{k=1}^{2}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\right)\sum_{c_{1}=t_{1}}^{1}\sum_{c_{2}=t_{2}}^{1}f(L,c_{1},c_{2})\prod_{j=1}^{2}g_{k}(L,x_{j},c_{j},c_{2})\dt
Using \eqref{abs-probabilities} we obtain the absorption probabilities
	&\mathcal{P}(0,0,\bm{\xi})=\frac{x_{1}(x_{2}-1)}{L(L+1)}\\
	&\mathcal{P}(0,1,\bm{\xi})=\frac{x_{1}(L+1-x_{2})}{L(L+1)}
\end{split}\quad \begin{split}
	&\mathcal{P}(1,0,\bm{\xi})=\frac{x_{2}(L+1-x_{1})}{L(L+1)}\\
	&\mathcal{P}(1,1,\bm{\xi})=\frac{(L-x_{1})(L+1-x_{2})}{L(L+1)}
where $\bm{\xi}=\delta_{a_{1}}^{x_{1}}+\delta_{a_{2}}^{x_{2}}$. 
Then, by using \eqref{exactCorrelations} we have 

@@

We consider the average with respect to $\mu^{NESS}$ of the occupation variable of the species  $a_{1},a_{2},a_{3}\in \{1,\ldots,N-1\}$ at coordinates $x_{1},x_{2},x_{3}\in \{1,\ldots,L\}$ such that $x_{1}<x_{2}<x_{3}$. Using \eqref{abs-probabilities} we compute the absorption probabilities 
	&\mathcal{P}(0,0,0,\bm{\xi})=\frac{x_{1}(x_{2}-1)(x_{3}-2)}{L(L^{2}-1)}\\
	&\mathcal{P}(1,0,0,\bm{\xi})=\frac{ x_{2} (x_3-1)(L-1)-x_1 (x_2-1)
		(x_3-2)}{L \left(L^2-1\right)}\\
	&\mathcal{P}(0,1,0,\bm{\xi})=\frac{x_1 (L (-x_3)+L+x_2 (x_3-2)+1)}{L(L^2-1)}\\
	&\mathcal{P}(0,0,1,\bm{\xi})=\frac{x_1 (x_2-1) (L-x_3+1)}{L \left(L^2-1\right)}
	\end{split}\quad \begin{split}
	&\mathcal{P}(1,1,0,\bm{\xi})=\frac{(L-1) x_2 (x_3-1)-x_1 (x_2-1)
		(x_3-2)}{L \left(L^2-1\right)}\\
	&\mathcal{P}(1,0,1,\bm{\xi})=\frac{(L-x_3+1) (x_2 (L-x_1-1)+x_1)}{L
		\left(L^2-1\right)}\\
	&\mathcal{P}(0,1,1,\bm{\xi})=\frac{x_1 (L-x_2) (L-x_3+1)}{L \left(L^2-1\right)}\\
	&\mathcal{P}(1,1,1,\bm{\xi})=\frac{(L-x_{1}-1)(L-x_{2})(L-x_{3}+1)}{L(L-1)(L+1)}
where $\bm{\xi}=\delta_{a_{1}}^{x_{1}}+\delta_{a_{2}}^{x_{2}}+\delta_{a_{3}}^{x_{3}}$ Then, by using \eqref{exactCorrelations} we obtain 
